Alone Together: Compositional Reasoning and Inference for Weak Isolation

### 2017-10-20 related-work.tex

Recent work by Crooks \emph{et al.}~\cite{CPA+17} also explores the
use of a state-based interpretation of isolation as we do, and share
our position that enables specification of weak isolation that are not
tied to implementation-specific artifacts.  However, they do not
consider verification (manual or automated) of client programs, and it
is not immediately apparent if their specification formalism is
amenable for use within a verification toolchain.

>>>>

Recent work by Crooks \emph{et al.}~\cite{CPA+17} also explores the
use of a state-based interpretation of isolation as we do, and share
our position that enables specification of weak isolation that are not
tied to implementation-specific artifacts.  However, they do not
consider verification (manual or automated) of client programs, and it
is not immediately apparent if their specification formalism is
amenable for use within a verification toolchain.  ~\cite{WB17}
presents a dynamic analysis for weak isolation that attempts to
discover weak isolation anomalies from SQL log files.  Their solution,
while capable of identifying database attacks due to the use of weaker
isolation levels than necessary, does not consider how to verify
application correctness, infer proper isolation levels, or formally
reason about the relationship between weak-isolation levels and
application invariants.
